Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-06-11 chapters/chapter-3.tex
Fix swap-in pseudocode

\begin{lstlisting}[language=C++, caption=Pseudocode \en{Swapping In} Teroptimisasi, label={lst:SwapInPseudocodeOptimized}]
tensor = stack.pop()
if (current_tensor.swapped) {
    swap_in(tensor, (gpu_tensor) => {
        current_tensor = gpu_tensor
    })
} else {
    current_tensor = tensor
}

>>>>

\begin{lstlisting}[language=C++, caption=Pseudocode \en{Swapping In} Teroptimisasi, label={lst:SwapInPseudocodeOptimized}]
tensor = stack.pop()
if (tensor.swapped) {
    swap_in(tensor, (gpu_tensor) => {
        current_tensor = gpu_tensor
    })
} else {
    current_tensor = tensor
}
